# Safety evaluation

```{r, include=params$log}
###
# study name: TIMCI
# program name: safety.Rmd  
# program purpose: Follow-up outcomes 
# author: Silvia Cicconi  
###
```

## Proportion of children who experienced a severe complication at any point during the study duration

The table below summarises severe complications (death or secondary hospitalisation) that occurred throughout the duration of the study.

```{r DEATHS SECONDARY HOS SUMMARY}


#yi
safety_summ_tab_yi <- onerow.sum.tab(as_label(d0[which(d0$yg_infant==1),]), vars=c("dth_flag", "hosp_noref", "hosp_refdel", "sev_comp"), vars_name=c("Deaths", "Hospitalisations without referral", "Hospitalisations with referral but delayed", "Severe complications"), by="pre_post")

#ch
safety_summ_tab_ch <- onerow.sum.tab(as_label(d0[which(d0$yg_infant==0),]), vars=c("dth_flag", "hosp_noref", "hosp_refdel", "sev_comp"), vars_name=c("Deaths", "Hospitalisations without referral", "Hospitalisations with referral but delayed", "Severe complications"), by="pre_post")


```

### Deaths and secondary hospitalisations summary - infants under 2 months of age

```{r, results='asis'}

knitr::kable(safety_summ_tab_yi, row.names = F) 

```

### Deaths and secondary hospitalisations summary - children 2-59 months of age

```{r, results='asis'}

knitr::kable(safety_summ_tab_ch, row.names = F) 

```
