```{r, include=params$log}
###
# study name: TIMCI
# program name: secondary_out.Rmd  
# program purpose: Summary of seconday outcomes modelling
# author: Silvia Cicconi  
###
```



# Summary of secondary outcomes results

Similarly to primary outcomes, the secondary outcomes are assessed using generalised estimating equation for logistic regression, with facilities as clusters.  Estimates for the pre-post effect on the outcomes are shown in terms of odds ratios and risk difference (with the pre-intervention period being the reference category) and their associated 95% confidence intervals. Results from both univariate and multivariate models are presented when numbers allowed. Not estimable intervention effects are denoted in the summary table below as "NE".

Multivariate models are adjusted for age, sex, travel time to facility, illness duration, previous care and treatment, cough, fever, diarrhoea and danger signs.




### Summary of secondary outcomes results - infants under 2 months of age

```{r, results='asis'}

knitr::kable(mod.sum.so_yi, row.names = F)

```



### Summary of secondary outcomes results - children 2-59 months of age

```{r, results='asis'}

knitr::kable(mod.sum.so, row.names = F)

```

