
# Antibiotic-related secondary outcomes

```{r, include=params$log}
###
# study name: TIMCI
# program name: antibio_antimal_out.Rmd  
# program purpose: Antibiotics and antimalarial related outcomes
# author: Silvia Cicconi  
###
```



## Proportion of children prescribed with an antibiotic at Day0

For the antibiotic-related outcomes, only antibacterials for systemic use are taken into account.

### Antibiotics prescription summary 

```{r ANTIBIOTICS PRESCRIPTION SUM}

tab_antibio <- sum.tab(d0, "antibio_flag", "intervention")

```

```{r, results='asis'}

knitr::kable(tab_antibio, row.names = F) 

```


## Proportion of children prescribed a diagnosis-appropriate antibiotic

Appropriateness of antibiotic prescription in relation to diagnosis is evaluated in different ways, considering only cases where a single diagnosis was provided.

The table below summarises the proportion of children who received a diagnosis for which a systemic antibiotic was indicated and a systemic antibiotic was prescribed. Only children with a diagnosis for which a systemic antibiotic was indicated are included in the denominator.


### Diagnosis-appropriate systemic antibiotic prescription summary

```{r ANTIBIOTIC APPROPRIATENESS SUM}

#prescribed when diagnosis required
tab_antibio_app <- sum.tab(d0[which( d0$single_diag==1 & d0$antibio_req==1),], "antibio_app", "intervention")


```

```{r, results='asis'}

knitr::kable(tab_antibio_app, row.names = F)

```

The table below summarises the proportion of children who received a diagnosis for which a systemic antibiotic was not indicated and a systemic antibiotic was prescribed. Only children with a diagnosis for which a systemic antibiotic was not indicated are included in the denominator.

### Diagnosis-inappropriate systemic antibiotic prescription summary

```{r ANTIBIOTIC INAPPROPRIATENESS SUM}

#prescribed when diagnosis not required
tab_antibio_unapp <- sum.tab(d0[which(d0$single_diag==1 & d0$antibio_req==0),], "antibio_unapp", "intervention")


```

```{r, results='asis'}

knitr::kable(tab_antibio_unapp, row.names = F)

```

The table below summarises the proportion of children who received first-line antibiotics according to recommendation for IMCI diagnosis for which specific antibiotic(s) are indicated. Only children who received an IMCI diagnosis requiring specific antibiotics will be counted in the denominator.

### Diagnosis-appropriate first-line systemic antibiotic prescription summary

```{r ANTIBIOTIC APPROPRIATENESS FIRST LINE}

#prescribed first line
tab_antibio_first_line <- sum.tab(d0[which(!is.na(d0$antibio_first_line)),], "antibio_first_line", "intervention")

```

```{r, results='asis'}

knitr::kable(tab_antibio_first_line, row.names = F)

```

# Antimalarial-related secondary outcomes

These secondary outcomes are only described for children 2 to 59 months of age.

## Proportion of febrile children tested for malaria at Day0

Only febrile children are counted in the denominator.

### Febrile children tested for malaria summary

```{r FEBRILE CHILDREN TESTED FOR MALARIA}

##proportion of febrile children (denominator) tested for malaria
tab_feb_mal <- sum.tab(d0[which(d0$fev_flag==1),], "mal_flag", "intervention")

#remove yg infants
tab_feb_mal <- tab_feb_mal[which(tab_feb_mal[,1]=="2-59 months of age"):nrow(tab_feb_mal),]

```

```{r, results='asis'}

knitr::kable(tab_feb_mal, row.names = F) 

```

## Proportion of malaria positive children prescribed an antimalarial

Only children with a positive malaria test are counted in the denominator.

### Malarial prescription for malaria positive children summary

```{r ANTIMALARIAL FOR POSITIVE MALARIA}

##proportion of positive malaria children (denominator) prescribed with antimalarial
tab_pos_mal <- sum.tab(d0[which(d0$mal_flag==1 & d0$malaria_res==1),], "antimal_flag", "intervention")

#remove yg infants
tab_pos_mal <- tab_pos_mal[which(tab_pos_mal[,1]=="2-59 months of age"):nrow(tab_pos_mal),]

```

```{r, results='asis'}

knitr::kable(tab_pos_mal, row.names = F) 

```

## Proportion of malaria negative children prescribed an antimalarial

Only children with a negative malaria test are counted in the denominator.

### Malarial prescription for malaria negative children summary

```{r ANTIMALARIAL FOR NEGATIVE MALARIA}

##proportion of negative malaria children (denominator) prescribed with antimalarial
tab_neg_mal <- sum.tab(d0[which(d0$mal_flag==1 & d0$malaria_res==0),], "antimal_flag", "intervention")

#remove yg infants
tab_neg_mal <- tab_neg_mal[which(tab_neg_mal[,1]=="2-59 months of age"):nrow(tab_neg_mal),]

```

```{r, results='asis'}

knitr::kable(tab_neg_mal, row.names = F) 

```

## Proportion of untested children prescribed an antimalarial

Only children untested for malaria test are counted in the denominator.

### Malarial prescription for untested children summary

```{r ANTIMALARIAL FOR UNTESTED CHILDREN}

##proportion of positive malaria children (denominator) prescribed with antimalarial
tab_un_mal <- sum.tab(d0[which(d0$mal_flag==0),], "antimal_flag", "intervention")

#remove yg infants
tab_un_mal <- tab_un_mal[which(tab_un_mal[,1]=="2-59 months of age"):nrow(tab_un_mal),]

#modelling

```

```{r, results='asis'}

knitr::kable(tab_un_mal, row.names = F) 

```
