
```{r, include=params$log}
###
# study name: TIMCI
# program name: baseline.Rmd  
# program purpose: summary of baseline characteristics 
# author: Silvia Cicconi  
# inputs: Datasets and codebooks  
# output(s): Datasets with additional derived variables 
# note: check git information for date, version and modification history
###
```

# Baseline characteristics

```{r THREE MOST COMMON SYMPTOMS}

##Select three most common symptoms for baseline table
#check codebooks for previous hospitalisation
d0_cb_in[which(d0_cb_in$db_name=="sx_var"), c("db_name", "label", "value", "category")]
d0_cb_tz[which(d0_cb_tz$db_name=="sx_var"), c("db_name", "label", "value", "category")]

#generate separate variables for multiple recorded symptoms
sx_var_temp_yi <- str_split(d0$sx_var[which(d0$yg_infant==1)], ";", simplify = T) #split all possible op in separate variables
sx_var_temp_ch <- str_split(d0$sx_var[which(d0$yg_infant==0)], ";", simplify = T) #split all possible op in separate variables

#save names of the three most common symptoms (except "other" and "none of the above")
list_sx_yi <- names(sort(table(sx_var_temp_yi), decreasing = T)); list_sx_yi <- list_sx_yi[which(!list_sx_yi%in%c("","96","99"))]; list_sx_yi <- list_sx_yi[1:3]; list_sx_yi
list_sx_ch <- names(sort(table(sx_var_temp_ch), decreasing = T)); list_sx_ch <- list_sx_ch[which(!list_sx_ch%in%c("","96","99"))]; list_sx_ch <- list_sx_ch[1:3]; list_sx_ch

#generate variables
for(i in list_sx_yi){
  d0[, paste("sx_yi", `i`, sep="_")] <- 0
  d0[which(d0$sx_var%in%c(d0$sx_var[grep(`i`,d0$sx_var)])), paste("sx_yi", `i`, sep="_")] <- 1
  d0[, paste("sx_yi", `i`, sep="_")] <- factor(d0[, paste("sx_yi", `i`, sep="_")])
}
for(i in list_sx_ch){
  d0[, paste("sx_ch", `i`, sep="_")] <- 0
  d0[which(d0$sx_var%in%c(d0$sx_var[grep(`i`,d0$sx_var)])), paste("sx_ch", `i`, sep="_")] <- 1
  d0[, paste("sx_ch", `i`, sep="_")] <- factor(d0[, paste("sx_ch", `i`, sep="_")])
}


```

### Baseline characteristics summary 

```{r BASELINE TABLE}

##combined
bsl_tab <- bs.sum(as_label(d0[, c("age_mo", "yg_infant", "who_age_ctg", "sex", "main_cg_der", "trans_time_der", "sick_duration_mod", "prev_care_yhf_der", "prev_care_nhf_der", "prev_care_no_der", "prev_care_un_der",
                         "prev_trt_ab_der", "prev_trt_am_der", "prev_trt_om_der", "prev_trt_oh_der", "prev_trt_ou_der", "prev_trt_no_der", "prev_trt_un_der", "prev_hosp_der")]), as_label(d0$intervention), 
                  names=c("Age (months)*", "Age subgroups", "Age (WHO categories)", "Sex", "Main caregiver", "Travel time to facility", "Illness duration", "Previous care for current illness**", rep("dummy", 3), "Previous treatment for current illness**", rep("dummy", 6), "Previous hospitalisation"), med.c=T, mean.c=F, minmax.c=F, tot=F, dig=F)

##by country
for(i in country_list){
  
  assign(paste("bsl_tab", `i`, sep="_"), bs.sum(as_label(d0[which(d0$country==`i`), c("age_mo", "yg_infant", "who_age_ctg", "sex", "main_cg_der", "trans_time_der", "sick_duration_mod", "prev_care_yhf_der", "prev_care_nhf_der", "prev_care_no_der", "prev_care_un_der",
                         "prev_trt_ab_der", "prev_trt_am_der", "prev_trt_om_der", "prev_trt_oh_der", "prev_trt_ou_der", "prev_trt_no_der", "prev_trt_un_der", "prev_hosp_der")]), as_label(d0$intervention[which(d0$country==`i`)]), 
                  names=c("Age (months)*", "Age subgroups", "Age (WHO categories)", "Sex", "Main caregiver", "Travel time to facility", "Illness duration", "Previous care for current illness**", rep("dummy", 3), "Previous treatment for current illness**", rep("dummy", 6), "Previous hospitalisation"), med.c=T, mean.c=F, minmax.c=F, tot=F, dig=F))

}


#adjust labels in country-specific tables
bsl_tab_in[,c(1,2)] <- bsl_tab[,c(1,2)]; bsl_tab_tz[,c(1,2)] <- bsl_tab[,c(1,2)]


#remove dummies
bsl_tab <- bsl_tab[-which(bsl_tab$`Statistics/Categories`=="dummy"),]
bsl_tab$Variables[which(bsl_tab$Variables=="dummy")] <- ""

bsl_tab_in <- bsl_tab_in[-which(bsl_tab_in$`Statistics/Categories`=="dummy"),]
bsl_tab_in$Variables[which(bsl_tab_in$Variables=="dummy")] <- ""

bsl_tab_tz <- bsl_tab_tz[-which(bsl_tab_tz$`Statistics/Categories`=="dummy"),]
bsl_tab_tz$Variables[which(bsl_tab_tz$Variables=="dummy")] <- ""

#replace intervention label with column names
names(bsl_tab_in)[c(3:5)] <- paste(get_labels(d0$intervention), substr(names(bsl_tab_in)[c(3:5)], 3, nchar(names(bsl_tab_in)[c(3:5)])))

names(bsl_tab_tz)[c(3:5)] <- paste(get_labels(d0$intervention), substr(names(bsl_tab_tz)[c(3:5)], 3, nchar(names(bsl_tab_tz)[c(3:5)])))

#drop CDSA column for combined and India
bsl_tab <- bsl_tab[,-ncol(bsl_tab)]
bsl_tab_in <- bsl_tab_in[,-ncol(bsl_tab_in)]

###check age category if numerical age is missing
table(d0$who_age_ct[which(is.na(d0$age_mo))], d0$country[which(is.na(d0$age_mo))])

```

```{r, results='asis'}

knitr::kable(bsl_tab, row.names = F) 

```

*Children whose month of birth was unknown are classified in the 60-364 days (3) and in the 12 to 59 months (12) WHO categories. \
**These questions allowed for multiple answers, therefore options are not mutually exclusive.


### Baseline characteristics summary - India

```{r, results='asis'}

knitr::kable(bsl_tab_in, row.names = F) 

```

*Children whose month of birth was unknown are classified in the 60-364 days (3) and in the 12 to 59 months (11) WHO categories.\
**These questions allowed for multiple answers, therefore options are not mutually exclusive.

### Baseline characteristics summary - Tanzania

```{r, results='asis'}

knitr::kable(bsl_tab_tz, row.names = F) 

```

*The child whose month of birth was unknown is classified in the 12 to 59 months WHO category. \
**These questions allowed for multiple answers, therefore options are not mutually exclusive.


```{r SIGNS AND SYMPTOMS ALL CHILDREN}

##combined
bsl_pres_tab <- bs.sum(as_label(d0[, c("danger_sign","sx_convulsions", "sx_lethargy", "vomit_ev_der", "eat_drink_der", "sx_cough", "sx_cough_onset", "sx_difficulty_breath", "sx_difficulty_breath_onset", "sx_diarrhoea", "sx_diarrhoea_onset", "sx_fever", "sx_fever_onset", "sx_vomit", "sx_less_feed")]), as_label(d0$intervention), 
                  names=c("At least one danger sign", "Convulsions", "Lethargic or unconscious", "Vomiting everything", "Completely unable to eat or drink", "Cough", "Cough duration (days)**", "Difficult breathing/rapid breathing", "Difficult breathing/rapid breathing (days)**", "Diarrhoea", "Diarrhoea duration (days)**", "Fever", "Fever duration (days)**", "Vomiting", "Eating or breastfeeding less than usual"), med.c=T, mean.c=F, minmax.c=F, tot=F, dig=F)

##by country
for(i in country_list){
  
  assign(paste("bsl_pres_tab", `i`, sep="_"), bs.sum(as_label(d0[which(d0$country==`i`), c("danger_sign","sx_convulsions", "sx_lethargy", "vomit_ev_der", "eat_drink_der", "sx_cough", "sx_cough_onset", "sx_difficulty_breath", "sx_difficulty_breath_onset", "sx_diarrhoea", "sx_diarrhoea_onset", "sx_fever", "sx_fever_onset", "sx_vomit", "sx_less_feed")]), as_label(d0$intervention[which(d0$country==`i`)]), 
                  names=c("At least one danger sign", "Convulsions", "Lethargic or unconscious", "Vomiting everything", "Completely unable to eat or drink", "Cough", "Cough duration (days)**", "Difficult breathing/rapid breathing", "Difficult breathing/rapid breathing (days)**", "Diarrhoea", "Diarrhoea duration (days)**", "Fever", "Fever duration (days)**", "Vomiting", "Eating or breastfeeding less than usual"), med.c=T, mean.c=F, minmax.c=F, tot=F, dig=F))

}


#adjust labels in country-specific tables
bsl_pres_tab_in[,c(1,2)] <- bsl_pres_tab[,c(1,2)]; bsl_pres_tab_tz[,c(1,2)] <- bsl_pres_tab[,c(1,2)]

#remove "unknown" for continuous variables (only collected for those who answered "yes")
bsl_pres_tab <- bsl_pres_tab[-(which(grepl("\\*", bsl_pres_tab$Variables)==T)+1),]
bsl_pres_tab_in <- bsl_pres_tab_in[-(which(grepl("\\*", bsl_pres_tab_in$Variables)==T)+1),]
bsl_pres_tab_tz <- bsl_pres_tab_tz[-(which(grepl("\\*", bsl_pres_tab_tz$Variables)==T)+1),]

#replace intervention label with column names
names(bsl_pres_tab_in)[c(3:5)] <- paste(get_labels(d0$intervention), substr(names(bsl_pres_tab_in)[c(3:5)], 3, nchar(names(bsl_pres_tab_in)[c(3:5)])))
names(bsl_pres_tab_tz)[c(3:5)] <- paste(get_labels(d0$intervention), substr(names(bsl_pres_tab_tz)[c(3:5)], 3, nchar(names(bsl_pres_tab_tz)[c(3:5)])))

#drop CDSA column for combined and India
bsl_pres_tab <- bsl_pres_tab[,-ncol(bsl_pres_tab)]
bsl_pres_tab_in <- bsl_pres_tab_in[,-ncol(bsl_pres_tab_in)]

```

### Signs and symptoms at presentations summary - combined, all children

```{r, results='asis'}

knitr::kable(bsl_pres_tab, row.names = F) 

```

**These are only evaluated for children presenting with the referenced sign/symptom.

### Signs and symptoms at presentations summary - India, all children

```{r, results='asis'}

knitr::kable(bsl_pres_tab_in, row.names = F) 

```

**These are only evaluated for children presenting with the referenced sign/symptom.

### Signs and symptoms at presentations summary - Tanzania, all children

```{r, results='asis'}

knitr::kable(bsl_pres_tab_tz, row.names = F) 

```

**These are only evaluated for children presenting with the referenced sign/symptom.



### Signs and symptoms at presentations summary - Infants under 2 months of age

Please note that although the report refers to infants under 2 months of age, from the data young infants are defined from 1 to < 60 days. 

```{r SIGNS AND SIMPTOMS AT PRESENTATION YOUNG INFANTS}

bsl_pres_yi_tab <- onerow.sum.tab(d0[which(d0$yg_infant==1),], vars=c("danger_sign", "sx_convulsions", "sx_lethargy", "vomit_ev_der", "eat_drink_der", "sx_cough", "sx_cough_onset", "sx_difficulty_breath", "sx_difficulty_breath_onset", "sx_diarrhoea", "sx_diarrhoea_onset", "sx_fever", "sx_fever_onset", "sx_vomit", "sx_less_feed", "sx_yi_2", "sx_yi_5", "sx_yi_10"), vars_name=c("At least one danger sign", "Convulsions", "Lethargic or unconscious", "Vomiting everything", "Completely unable to eat or drink", "Cough", "Cough duration (days)**", "Difficult breathing/rapid breathing", "Difficult breathing/rapid breathing (days)**", "Diarrhoea", "Diarrhoea duration (days)**", "Fever", "Fever duration (days)**", "Vomiting", "Eating or breastfeeding less than usual", "Runny nose / cold", "Skin problem", "Abdominal pain"), by="intervention")

```

```{r, results='asis'}

knitr::kable(bsl_pres_yi_tab, row.names = F) 

```

**These are only evaluated for children presenting with the referenced sign/symptom.

### Signs and symptoms at presentations summary - Children 2-59 months of age

Please note that although the report refers to 2-59 months of age, from the data children are defined from 60 days to <= 59 months. 

```{r SIGNS AND SIMPTOMS AT PRESENTATION OLDER CHILDREN}

bsl_pres_ch_tab <- onerow.sum.tab(d0[which(d0$yg_infant==0),], vars=c("danger_sign", "sx_convulsions", "sx_lethargy", "vomit_ev_der", "eat_drink_der", "sx_cough", "sx_cough_onset", "sx_difficulty_breath", "sx_difficulty_breath_onset", "sx_diarrhoea", "sx_diarrhoea_onset", "sx_fever", "sx_fever_onset", "sx_vomit", "sx_less_feed", "sx_ch_2", "sx_ch_5", "sx_ch_10"), vars_name=c("At least one danger sign", "Convulsions", "Lethargic or unconscious", "Vomiting everything", "Completely unable to eat or drink", "Cough", "Cough duration (days)**", "Difficult breathing/rapid breathing", "Difficult breathing/rapid breathing (days)**", "Diarrhoea", "Diarrhoea duration (days)**", "Fever", "Fever duration (days)**", "Vomiting", "Eating or breastfeeding less than usual", "Runny nose / cold", "Skin problem", "Abdominal pain"), by="intervention")

#replace with "-" CDSA for India
bsl_pres_ch_tab[which(bsl_pres_ch_tab[,1]=="India"), ncol(bsl_pres_ch_tab)] <- "-"

```

```{r, results='asis'}

knitr::kable(bsl_pres_ch_tab, row.names = F) 

```

**These are only evaluated for children presenting with the referenced sign/symptom.









